---
title: "Covid wider impacts dashboard - Google analytics report"
author: "PHS"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r TODO, include = FALSE}
# Add tables/downloadable data?
# Anything else to add to report
# Schedule it to run every month

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F) # prevents code to be shown in report

#Packages
library(dplyr)
library(plotly)
library(knitr)
```

```{r env}
data_folder <- "/conf/PHSCOVID19_Analysis/shiny_input_files/google_analytics/"

sessions <- readRDS(paste0(data_folder, "sessions.rds"))
tabvisits <- readRDS(paste0(data_folder, "tabvisits.rds"))
device <- readRDS(paste0(data_folder, "device.rds"))
source <- readRDS(paste0(data_folder, "source.rds"))

```

```{r plot_parameter}

# Style of x and y axis
xaxis_plots <- list(title = FALSE, tickfont = list(size=14), 
                    titlefont = list(size=14),
                    showline = TRUE, fixedrange=TRUE,
                    rangeslider = list(type = "date", thickness = 0.075
         # Without this, range will change when adding/removing markers
                                       ))

yaxis_plots <- list(title = "Number of visits", rangemode="tozero", 
                    fixedrange=TRUE, size = 4,
                    tickfont = list(size=14), titlefont = list(size=14))

# Buttons to remove
bttn_remove <-  list('select2d', 'lasso2d', 'zoomIn2d', 'zoomOut2d',
                     'autoScale2d',   'toggleSpikelines',  'hoverCompareCartesian',
                     'hoverClosestCartesian', 'zoom2d', 'pan2d', 'resetScale2d') 

  # For annotation
  zoom_hover_text =
    "Drag the markers at either end of<br>the bar to view specific time periods"

  # We need an annotation to show user how to use the rangeslider
  zoom_annotation =
    list(text = "Drag to zoom", borderpad = 2,
         hovertext = zoom_hover_text,
         showarrow = TRUE, ax = 0, ay = 18,
         x = 0, xref = "paper", xanchor = "left",
         y = -0.35, yref = "paper", yanchor = "middle")
  
    # Annotation to mark when 
  monthly_annotation =
    list(text = "Drag to zoom", borderpad = 2,
         hovertext = zoom_hover_text,
         showarrow = TRUE, ax = 0, ay = 18,
         x = 0, xref = "paper", xanchor = "left",
         y = -0.35, yref = "paper", yanchor = "middle")
  
      # Function for verical line at start of lockdown
    vline <- function(x = 0, color = "lightgrey") {
      list(
        type = "line",
        y0 = 0,
        y1 = 1,
        yref = "paper",
        x0 = x,
        x1 = x,
        line = list(color = color, dash = 'dash')
      )
    }
  
###############################################.
# Palettes 
  
pal_pregbab <- c('#E39C8C', '#d4d3d5', '#83BB26', '#80BCEA', '#3F3685', '#8FBFC2',
             '#6B5C85', '#0078D4', '#C1DD93')  
pal_cancer <- c('#4da6ff','#ffa64d') 
pal_ch <- c('#000000', '#4da6ff','#ffa64d')
pal_other <- c('#4da6ff','#ffa64d', '#2c7fb8', '#7fcdbb', '#a3a3c2', '#FF0000')




```

```{r plot_function}
#Plot function for tabs data
plot_tab <- function(x, pal_chose) {
  
  tooltip_plot <- c(paste0(x$tabname, "<br>",
                            x$week_ending, "<br>",
                            "Visits: ", x$count))
  
  plot_ly(x, x = ~week_ending) %>% 
    add_trace(y = ~count, color = ~tabname,
              colors = pal_chose,
              type = "scatter", mode = "lines+markers",
              text=tooltip_plot, hoverinfo="text") %>% 
      #Layout
      layout(yaxis = yaxis_plots, xaxis = xaxis_plots,
             margin = list(b = 80, t = 5, r = 25), # to avoid labels getting cut off
             annotations = zoom_annotation) %>% 
      # leaving only save plot button
      config(displaylogo = F, displayModeBar = TRUE, 
             modeBarButtonsToRemove = bttn_remove )
}

```

This reports shows the visits to the Covid wider impacts dashboard and each one
of their tabs. Tab visits data is only available from 4 February 2022 onwards. Overall visits data is available from 26 June 2020.

## Number of sessions over the last year

```{r overall}
kable(device)
```

## Overall visits to the dashboard

```{r sessions}
#Tooltip for the sessions chart
tooltip_sess <- c(paste0(sessions$week_ending, "<br>",
                         "Visits: ", sessions$count))

# Plot for the overall visits
plot_ly(sessions) %>% 
  add_lines(x = ~week_ending, y = ~count,
            text=tooltip_sess, hoverinfo="text") %>% 
  # Annotation to mark
      add_annotations(x = "2020-11-01",
                      y = ~max(count),
                      text = "Move from weekly to monthly updates",
                      xref = "1", yref = "1", showarrow = F) %>% 
  layout(yaxis = yaxis_plots, xaxis = xaxis_plots,
          shapes = list(vline("2020-11-01")), #for annotation
         margin = list(b = 80, t = 5, r = 25), # to avoid labels getting cut off
         annotations = zoom_annotation) %>% 
  # leaving only save plot button
  config(displaylogo = F, displayModeBar = TRUE, 
             modeBarButtonsToRemove = bttn_remove )

```

## Visits per tab

### Pregnancy, births and babies tabs

```{r pregbirthbaby}
plot_tab(tabvisits[["Pregnancy/births/babies"]], pal_chose = pal_pregbab)
```

### Child health tabs

```{r childhealth}
plot_tab(tabvisits[["Child health"]], pal_chose = pal_ch)
```

### Cancer tabs

```{r cancer}
plot_tab(tabvisits[["Cancer"]], pal_chose = pal_cancer)
```

### Substance use tab

```{r subst}
plot_tab(tabvisits[["Substance use"]], pal_chose = c("blue"))
```

### Other tabs

```{r others}
plot_tab(tabvisits[["Others"]], pal_chose = pal_other)
```

## Average session time

```{r ave_sess}


#Tooltip for the sessions chart
tooltip_sess <- c(paste0(sessions$week_ending, "<br>",
                         "Average minutes: ", sessions$session_ave))

# Plot for the overall visits
plot_ly(sessions) %>% 
  add_lines(x = ~week_ending, y = ~session_ave,
            text=tooltip_sess, hoverinfo="text") %>% 
  # Annotation to mark
      add_annotations(x = "2020-11-01",
                      y = ~max(session_ave),
                      text = "Move from weekly to monthly updates",
                      xref = "1", yref = "1", showarrow = F) %>% 
  layout(yaxis = list(yaxis_plots, title = "Average minutes"), xaxis = xaxis_plots,
          shapes = list(vline("2020-11-01")), #for annotation
         margin = list(b = 80, t = 5, r = 25), # to avoid labels getting cut off
         annotations = zoom_annotation) %>% 
  # leaving only save plot button
  config(displaylogo = F, displayModeBar = TRUE, 
             modeBarButtonsToRemove = bttn_remove )

```

## Top 20 sources of visits over the last year

```{r source}
kable(source)
```

